### 2016-02-09 mcmc.tex
2 hoggs

What are your best options for the ``uncertainty'' or ``limits'' on this parameter?
The only simple integral-based options are either variances or else posterior quantiles.
We usually use quantiles.
That is, the ``one-sigma'' error bar can be taken to be the half-size of the central (or smallest%
  \note{HOGG shizzle about choosing quantiles}) interval of the parameter
  that contains 68 percent of the posterior samples.
The ``two-sigma'' error bar would be the same but for the 95-percent interval.
Again, these limits can be estimated%
  \note{One amusing thing about samplings,
  which are so beloved of us probabilistic (Bayesian) reasoners,
  is that anything we \emph{do} with a sampling,
  like estimate an integral or a quantile,
  is just an old-school frequentist estimator.
  A frequentist estimator of a Bayesian quantity, to be sure, but a frequentist estimator nonetheless.}
  by ordering the $q(\pars_k)$ values,
  and finding the $\pars$ values such that some fraction (0.68 or 0.95)
  of the samples lie between them.
Again, to form these limits, $q(\pars)$ must be a scalar function (so sorting is well defined).

@@

In principle the only output from the sampling that safely gives both
probabilistic information about the result of the inference and also
good-fitting models is a few---randomly chosen---example samples.
We strongly recommend this\note{HOGG:  And we do this WHERE? Cite Lang, cite eccentricity; etc??};
in particular this is a better thing to do
than to give the ``best sample'', which isn't even guaranteed to be
near the bulk of the posterior pdf or the samples therefrom.

@@

\clearpage
\raggedright
\begin{thebibliography}{}\markright{References}
\bibitem[Box \& Draper(1987)]{box}
  Box,~G.~E.~P. \& Draper,~N.~R.\ 1987,
  \textit{Empirical Model Building and Response Surfaces},
  John Wiley \& Sons, New York, NY
  \isbn{978-0471810339}.
\bibitem[Brooks \etal(2011)]{mcmchandbook}
  Brooks,~S., Gelman~A., Jones~G., \& Meng,~X.-L., eds.\ 2011,
  \href{http://www.mcmchandbook.net/HandbookTableofContents.html}{\textit{Handbook of Markov Chain Monte Carlo}},
  Chapman and Hall~/~CRC Press
  \isbn{978-1-4200-7941-8}.
\bibitem[Foreman-Mackey \etal(2012)]{emcee}
  Foreman-Mackey,~D., Hogg,~D.~W., Lang,~D., \& Goodman,~J.\ 2012,
  \project{emcee}: The \MCMC\ Hammer,
  \textit{Pubs.\,Astron.\,Soc.\,Pac.}\ \textbf{125} 306--312
  \doi{10.1086/670067}
  (also \arxiv{1202.3665}).
\bibitem[Geisser(1993)]{crossval}
  Geisser,~S., 1993,
  \textit{Predictive Inference: An Introduction},
  Chapman \& Hall
  \isbn{978-0412034718}.
\bibitem[Gelman \etal(1996a)]{ppcheck}
  Gelman,~A., Meng,~X.-L., \& Stern,~H., 1996a,
  \href{http://www.jstor.org/stable/24306036}{Posterior predictive assessment of model fitness via realized discrepancies},
  \textit{Statistica Sinica}, \textbf{6}(4) 733--760.
\bibitem[Gelman \etal(1996b)]{gelman234}
  Gelman,~A., Roberts,~G.~O., \& Gilks,~W.~R., 1996b,
  \href{http://www.stat.columbia.edu/~gelman/research/published/baystat5.pdf}{Efficient Metropolis jumping rules},
  in Bernardo,~J.~M, Berger,~J.~O., Dawid,~A.~P., \& Smith,~A.~F.~M, eds.,
  \textit{Bayesian Statistics} \textbf{5}, Oxford University Press
  599--607.
\bibitem[Geyer(2011)]{geyer}
  Geyer,~C.~J., 2011,
  \href{http://www.mcmchandbook.net/HandbookChapter1.pdf}{Introduction to Markov Chain Monte Carlo},
  in \citet{mcmchandbook}, 3--48.
\bibitem[Hogg \etal(2010a)]{fittingaline}
  Hogg,~D.~W., Bovy,~J., \& Lang,~D., 2010a,
  Data analysis recipes: Fitting a model to data,
  \arxiv{1008.4686v1}.
\bibitem[Hogg \etal(2010b)]{eccentricity}
  Hogg,~D.~W., Myers,~A.~D., \& Bovy,~J., 2010b,
  \href{http://adsabs.harvard.edu/abs/2010ApJ...725.2166H}{Inferring the eccentricity distribution},
  \textit{Astrophys.\ J.}\ \textbf{725}, 2166--2175.
\bibitem[Hou \etal(2014)]{fengji}
  Hou,~F., Goodman,~J., \& Hogg,~D.~W., 2014,
  The probabilities of orbital-companion models for stellar radial velocity data,
  \arxiv{1401.6128}.
\bibitem[Metropolis \etal(1953)]{metropolis}
  Metropolis,~N., Rosenbluth,~A.~W., Rosenbluth,~M.~N., Teller,~A.~H., \& Teller,~E., 1953,
  Equation of state calculations by fast computing machines,
  \textit{J.\ Chem.\ Phys.}, \textbf{21} 1087--1092.
\bibitem[Neal \etal(2011)]{hamiltonian}
  Neal,~R.~M., 2011,
  \href{http://www.mcmchandbook.net/HandbookChapter5.pdf}{\MCMC\ Using Hamiltonian Dynamics},
  in \citet{mcmchandbook}, 113--162.
\bibitem[Pasarica \& Gelman(2010)]{esjd}
  Pasarica,~C. \& Gelman,~A., 2010
  \href{http://www.jstor.org/stable/24308995}{Adaptively scaling the Metropolis algorithm using expected squared jumped distance},
  \textit{Statistica Sinica}, \textbf{20}(1) 343--364.
\bibitem[van~der~Walt \etal(2011)]{numpy}
  van~der~Walt,~S., Colbert,~S.~C., \& Varoquaux,~G., 2011,
  The NumPy Array: A structure for efficient numerical computation,
  \textit{Computing in Sci.\ \& Eng.}\ \textbf{13}, 22--30
  \doi{10.1109/MCSE.2011.37}.
\end{thebibliography}

>>>>

What are your best options for the ``uncertainty'' or ``limits'' on this parameter?
The only simple integral-based options are either variances or else posterior quantiles.
We usually use quantiles.
That is, the ``one-sigma'' error bar can be taken to be the half-size of the central (or smallest\note{%
  We usually create a 68-percent (or 95-percent) interval or region by
  excluding the top and bottom 16 percent (or 2.5 percent) of the
  posterior samples.  Some more aggressive investigators find the
  smallest interval that contains 68 (or 95) percent of the samples.
  Both are legitimate, and they are near-identical for distributions
  that are near-symmetric around the mean.})
  interval of the parameter that contains 68 percent of the posterior
  samples.
The ``two-sigma'' error bar would be the same but for the 95-percent interval.
Again, these limits can be estimated%
  \note{One amusing thing about samplings,
  which are so beloved of us probabilistic (Bayesian) reasoners,
  is that anything we \emph{do} with a sampling,
  like estimate an integral or a quantile,
  is just an old-school frequentist estimator.
  A frequentist estimator of a Bayesian quantity, to be sure, but a frequentist estimator nonetheless.}
  by ordering the $q(\pars_k)$ values,
  and finding the $\pars$ values such that some fraction (0.68 or 0.95)
  of the samples lie between them.
Again, to form these limits, $q(\pars)$ must be a scalar function (so sorting is well defined).
Because they are so afraid of being confused with frequentists,
Bayesians often call these regions ``credible'' rather than
``confidence''\note{We don't like this ``credible'' terminology,
  though we sometimes adopt it to avoid confusion.}

@@

In principle the only output from the sampling that safely gives both
probabilistic information about the result of the inference and also
good-fitting models is a few---randomly chosen---example samples.
We strongly recommend this\note{And we do it ourselves.  For examples,
  you can look at \citet{cometholmes} and \citet{exopop}.}; in
particular this is a better thing to do than to give the ``best
sample'', which isn't even guaranteed to be near the bulk of the
posterior pdf or the samples therefrom.

@@

\clearpage
\raggedright
\begin{thebibliography}{}\markright{References}
\bibitem[Box \& Draper(1987)]{box}
  Box,~G.~E.~P. \& Draper,~N.~R.\ 1987,
  \textit{Empirical Model Building and Response Surfaces},
  John Wiley \& Sons, New York, NY
  \isbn{978-0471810339}.
\bibitem[Brooks \etal(2011)]{mcmchandbook}
  Brooks,~S., Gelman~A., Jones~G., \& Meng,~X.-L., eds.\ 2011,
  \href{http://www.mcmchandbook.net/HandbookTableofContents.html}{\textit{Handbook of Markov Chain Monte Carlo}},
  Chapman and Hall~/~CRC Press
  \isbn{978-1-4200-7941-8}.
\bibitem[Foreman-Mackey \etal(2012)]{emcee}
  Foreman-Mackey,~D., Hogg,~D.~W., Lang,~D., \& Goodman,~J.\ 2012,
  \project{emcee}: The \MCMC\ Hammer,
  \textit{Pubs.\ Astron.\ Soc.\ Pac.}\ \textbf{125} 306--312
  \doi{10.1086/670067}
  (also \arxiv{1202.3665}).
\bibitem[Foreman-Mackey \etal(2014)]{exopop}
  Foreman-Mackey,~D., Hogg,~D.~W., \& Morton,~T.~D., 2014,
  \href{http://adsabs.harvard.edu/abs/2014ApJ...795...64F}{Exoplanet population
    inference and the abundance of earth analogs from noisy, incomplete catalogs},
  \textit{Astrophys.\ J.}\ \textbf{795} 64
  \doi{10.1088/0004-637X/795/1/64}.
\bibitem[Geisser(1993)]{crossval}
  Geisser,~S., 1993,
  \textit{Predictive Inference: An Introduction},
  Chapman \& Hall
  \isbn{978-0412034718}.
\bibitem[Gelman \etal(1996a)]{ppcheck}
  Gelman,~A., Meng,~X.-L., \& Stern,~H., 1996a,
  \href{http://www.jstor.org/stable/24306036}{Posterior predictive assessment of model fitness via realized discrepancies},
  \textit{Statistica Sinica}, \textbf{6}(4) 733--760.
\bibitem[Gelman \etal(1996b)]{gelman234}
  Gelman,~A., Roberts,~G.~O., \& Gilks,~W.~R., 1996b,
  \href{http://www.stat.columbia.edu/~gelman/research/published/baystat5.pdf}{Efficient Metropolis jumping rules},
  in Bernardo,~J.~M, Berger,~J.~O., Dawid,~A.~P., \& Smith,~A.~F.~M, eds.,
  \textit{Bayesian Statistics} \textbf{5}, Oxford University Press
  599--607.
\bibitem[Geyer(2011)]{geyer}
  Geyer,~C.~J., 2011,
  \href{http://www.mcmchandbook.net/HandbookChapter1.pdf}{Introduction to Markov Chain Monte Carlo},
  in \citet{mcmchandbook}, 3--48.
\bibitem[Hogg \etal(2010a)]{fittingaline}
  Hogg,~D.~W., Bovy,~J., \& Lang,~D., 2010a,
  Data analysis recipes: Fitting a model to data,
  \arxiv{1008.4686v1}.
\bibitem[Hogg \etal(2010b)]{eccentricity}
  Hogg,~D.~W., Myers,~A.~D., \& Bovy,~J., 2010b,
  \href{http://adsabs.harvard.edu/abs/2010ApJ...725.2166H}{Inferring the eccentricity distribution},
  \textit{Astrophys.\ J.}\ \textbf{725} 2166--2175.
\bibitem[Hou \etal(2014)]{fengji}
  Hou,~F., Goodman,~J., \& Hogg,~D.~W., 2014,
  The probabilities of orbital-companion models for stellar radial velocity data,
  \arxiv{1401.6128}.
\bibitem[Lang \& Hogg(2012)]{cometholmes}
  Lang,~D. \& Hogg,~D.~W., 2012,
  \href{http://adsabs.harvard.edu/abs/2012AJ....144...46L}{Searching for comets on the World Wide Web:
    The orbit of 17P/Holmes from the behavior of photographers},
  \textit{Astron.\ J.}\ \textbf{144} 46
  \doi{10.1088/0004-6256/144/2/46}.
\bibitem[Metropolis \etal(1953)]{metropolis}
  Metropolis,~N., Rosenbluth,~A.~W., Rosenbluth,~M.~N., Teller,~A.~H., \& Teller,~E., 1953,
  Equation of state calculations by fast computing machines,
  \textit{J.\ Chem.\ Phys.}, \textbf{21} 1087--1092.
\bibitem[Neal \etal(2011)]{hamiltonian}
  Neal,~R.~M., 2011,
  \href{http://www.mcmchandbook.net/HandbookChapter5.pdf}{\MCMC\ Using Hamiltonian Dynamics},
  in \citet{mcmchandbook}, 113--162.
\bibitem[Pasarica \& Gelman(2010)]{esjd}
  Pasarica,~C. \& Gelman,~A., 2010
  \href{http://www.jstor.org/stable/24308995}{Adaptively scaling the Metropolis algorithm using expected squared jumped distance},
  \textit{Statistica Sinica}, \textbf{20}(1) 343--364.
\bibitem[van~der~Walt \etal(2011)]{numpy}
  van~der~Walt,~S., Colbert,~S.~C., \& Varoquaux,~G., 2011,
  The NumPy Array: A structure for efficient numerical computation,
  \textit{Computing in Sci.\ \& Eng.}\ \textbf{13}, 22--30
  \doi{10.1109/MCSE.2011.37}.
\end{thebibliography}
